{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-16 bmvc_review.tex
More HyperParameters Added

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing specific challenges in single,
target tracking problem. Thus each of them should have different
values for the optimal parameters. For instance, the primary task of
the translation filter, $R_{t}^{L}$ is to estimate the translation of
a target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. For our particle filter implementation, we empirically set the
number of particles to $1000$ to balance the run-time performance and
accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

@@

\textbf{Performance on UAV123 Dataset} We compared, using the
precision and success rate metrics, the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50): SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
MUSTER \cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ in 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny \textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

>>>>

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing specific challenges in single,
target tracking problem. Thus each of them should have different
values for the optimal parameters. For instance, the primary task of
the translation filter, $R_{t}^{L}$ is to estimate the translation of
a target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.012$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. Finally, the padding size for the correlation filters is tuned to $3$ for $R_{t}^{L}$, $2$ for $R_{t}^{S}$, 
and $1$ for $R_{s}$. For our particle filter implementation, we empirically set the
number of particles to $1000$ to balance the run-time performance and
accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

@@

\textbf{Performance on UAV123 Dataset} We compared, using the
precision and success rate metrics, the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF\cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50): SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
MUSTER \cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ in 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny\:\:\:\:\:\:\textbf{UAV123}\hspace{.44\linewidth}\:\:\:\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}
